Appendix

### 2019-12-03 manuscript/appendix.Rmd
explore data vs predicted plots

cowplot::plot_grid(
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tn)) + 
  ylab("TN (ug/L)") +
  xlab("Percent Agriculture"), 
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tp)) +
  ylab("TP (ug/L)") +
  xlab("Percent Agriculture")
)

>>>>

# fit_tn      <- lm(log(tn) ~ log(ag), data = dt)
# fit_tn_pred <- data.frame(tn = fit_tn$model$`log(tn)`, 
#                           tn_pred = fit_tn$fitted.values, 
#                           stringsAsFactors = FALSE)
# ggplot(data = fit_tn_pred) + 
#   geom_point(aes(x = tn, y = tn_pred)) +
#   geom_abline(slope = 1)
# 
# fit_tp      <- lm(log(tp) ~ log(ag), data = dt)
# fit_tp_pred <- data.frame(tp = fit_tp$model$`log(tp)`, 
#                           tp_pred = fit_tp$fitted.values, 
#                           stringsAsFactors = FALSE)
# ggplot(data = fit_tp_pred) + 
#   geom_point(aes(x = tp, y = tp_pred)) +
#   geom_abline(slope = 1)

cowplot::plot_grid(
ggplot(data = dt) + 
  geom_point(aes(x = log(ag), y = log(tn))) + 
  ylab("TN (ug/L)") +
  xlab("Percent Agriculture"), 
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tp)) +
  ylab("TP (ug/L)") +
  xlab("Percent Agriculture")
)
